My title

### 2024-02-12 paper/paper.qmd
small fix

# replicate figure 2d from the original paper
fig_2d_data_long %>% ggplot(aes(x = year, y = Birth_Rate, color = Education_Level)) +
  geom_line(size = 1) +
  labs(x = "Year", y = "", color = "Education Level", caption = "Mother’s level of education (ages 20–44)") +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 150, by = 20)) +
  scale_x_continuous(limits = c(1990, 2020), breaks = seq(1990, 2020, by = 5)) +
  geom_text(aes(x = 1995, y = 105), label = "No high school degree", color = "black") +
  geom_text(aes(x = 1995, y = 75), label = "College graduate
", color = "#d44215") +
  theme_classic() +
  geom_text(aes(x = 1995, y = 65), label = "High school graduate", color = "#0cc4be") +
  geom_text(aes(x = 1995, y = 45), label = "Some college", color = "black") +
  theme_classic() +
  theme(legend.position = "none")
```

>>>>

# replicate figure 2d from the original paper
fig_2d_data_long %>% ggplot(aes(x = year, y = Birth_Rate, color = Education_Level)) +
  geom_line(size = 1) +
  labs(x = "Year", y = "Births per 1,000 women in relevant population subgroup", color = "Education Level", caption = "Mother’s level of education (ages 20–44)") +
  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 150, by = 20)) +
  scale_x_continuous(limits = c(1990, 2020), breaks = seq(1990, 2020, by = 5)) +
  geom_text(aes(x = 1995, y = 105), label = "No high school degree", color = "black") +
  geom_text(aes(x = 1995, y = 75), label = "College graduate
", color = "#d44215") +
  theme_classic() +
  geom_text(aes(x = 1995, y = 65), label = "High school graduate", color = "#0cc4be") +
  geom_text(aes(x = 1995, y = 45), label = "Some college", color = "black") +
  theme_classic() +
  theme(legend.position = "none")
```
